### 2017-10-29 treestats_paper.tex
simpler alg

\paragraph{Total site weight algorithm}
This works as the \emph{total branch length weight algorithm} except that steps (5--6) are replaced with:
\begin{itemize}
    \item[5'] \emph{Find allele weights} for each mutated site in the tree:
        \begin{itemize}
            \item Find mutation weights: 
                    set $u[-1]$ to be the value of $x$ at the root,
                    and then for each mutated node $e$,
                \begin{itemize}
                    \item Set $u[e] = x[e]$ 
                    \item Find $p(e)$, the parent mutation of $e$
                        and update $u[p(e)] -= x[e]$.
                \end{itemize}
            \item Find allele weights: for each unique allele $a$ seen,
                set $v[a]$ to the sum of $u[e]$ across all $e$ with allele $a$.
                Then add $w(v)$ to $T$.
        \end{itemize}
\end{itemize}
\plr{check that algorithm deals correctly with more than one mut per node}

>>>>

\paragraph{Total site weight algorithm}
This works as the \emph{total branch length weight algorithm} except that steps (5--6) are replaced with:
\plr{gah this is terrible}
\begin{itemize}
    \item[5'] \emph{Find allele weights} for each mutated site in the tree:
        if $a$ is the ancestral allele,
        set $u[a]$ to be the value of $x$ at the root; and then,
        for each mutation at node $e$ with derived allele $b$ 
        and parent mutation occurring at node $p$ with derived allele $c$,
        add $x[e]$ to $u[b]$, and subtract $x[p]$ from $u[c]$.
    \item[6'] For each unique allele $a$ seen,
        add $w(v[a])$ to $T$.
\end{itemize}
\plr{check that algorithm deals correctly with more than one mut per node}
